`r paste(params$species)` biomass trends and figures

### 2019-11-28 analysis/VOCC/3-bioclimatic-trends.Rmd
update bioclimatic calculation

---
title: "`r paste(params$species)` biomass trends and figures"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Redbanded Rockfish"
    region: "All synoptic surveys"
    start_year: 2008
    bind_predictions: FALSE
    covs: "-log-both-noAR1" # covariate string used to name model rds 
---

@@

  predictions$est_exp <- exp(predictions$est) * 10000
  predictions$bioclimatic <- exp(predictions$est - predictions$epsilon_st) * 10000

>>>>

---
title: "`r paste(params$species)` biomass trends and figures"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Redbanded Rockfish"
    region: "All synoptic surveys"
    start_year: 2008
    bind_predictions: FALSE
    covs: "-AR1-spatial" 
    #covs: "-log-both-fixed-depth"
    #covs: "-log-both-noAR1" # covariate string used to name model rds 
---

@@

  predictions$est_exp <- exp(predictions$est) * 10000

  predictions <- predictions %>% group_by(X,Y) %>% arrange(year) %>% mutate(lag_epsilon = lag(epsilon_st), bioclimatic = est - epsilon_st + lag_epsilon)
